### 2025-11-29 multiple-regression.qmd
20251129 - covariate selection

>>>>

In general, you should select which covariates to include based on theory and your [causal diagram](#sec-causalDiagrams) of the causal process (as described in @sec-causalDiagrams), not based on whether the covariate has a [statistically significant](#sec-statisticalSignificance) association with the [outcome variable](#sec-correlationalStudy).
Just because a [predictor variable](#sec-correlationalStudy) is not associated with an [outcome variable](#sec-correlationalStudy) does not mean that the [predictor variable](#sec-correlationalStudy) will not be useful in the model.
For instance, the [predictor variable](#sec-correlationalStudy) could have a [suppression effect](#sec-multipleRegressionSuppression), or a [moderating effect](#sec-moderation), etc., that may not be detectable based on a bivariate association.
